Discrete Ordinates

### 2017-06-01 docprep/chapintro.tex
Reworded sections of the methods and fixed typos in the intro

Another, similar, application is dose estimation of patients receiving radiation therapy. Often, before the procedure, a time dependent, 4D CT scan of the patient is taken so that radiologists can account for breathing patterns during administration of the treatment [CITE]. With further develpment, this methodology may enable real time dose computation as the treatment is administered. This would be greatly beneficial to both patients and the doctors administering the procedure.

@@

Along any particular ray, monoenergetic particles will attenuate through a homogeneus media according to the Beer-Lambert law given in Eq.~\ref{eq:beer_lambert} [CITE] resulting in a small fraction of the source particles reaching the detector. This phenomena leads to an image of the attenutating media but also results in the detector receiving information about the attenuation coefficient, $\mu$, along that ray. With sufficient rays of varying directionality, the entire object can be quantified with respect to its spatially distributed attenuation coefficient. The Hounsfield units (also called CT numbers) are traditionally scaled such that -1000 is dry air and water is zero [CITE].

@@

Deterministic codes can be accelerated with the use of a grpahics processin gunit (GPU). GPUs differ from the central processin gunit (CPU) in that  each of th emany cores performes identical instruction to all others at the same time bue each with different data. For example, consider a grapyscale 1024$\times$768 image. If some pixelwise operation is applied on a CPU, 786,432 operations must occur. Onboard a GPU with 1024 cores, every pixel in the entire row can be computed simultaneously reducing the number of operations to 768. However, issues such as communication to and from the GPU and cache coherency problems can degrade performance. GPU tehcnology and performance is discussed more throuroughly in Section~\ref{sec:cuda}.

In addition to rapidly computing the patient dose, another goal of DOCTORS is to present the code in a user-friendly fashion. To this end, a grpahical user interface (GUI) was developed. The GUI utilize the Qt5 graphics framework for the window, buttons, and other necessary widgets. The GUI leads the user through the steps necessary to use the code in an intuitive way by using colors to indicated required and completed steps. The output is then plotted graphically as well as sent to an ASCII text file for more advanced postprocessing. More details about the GUI are included in Section~\ref{sec:gui}.

>>>>

Another, similar, application is dose estimation of patients receiving radiation therapy. Often, before the procedure, a time dependent, 4D CT scan of the patient is taken so that radiologists can account for breathing patterns during administration of the treatment [CITE]. With further development, this methodology may enable real time dose computation as the treatment is administered. This would be greatly beneficial to both patients and the doctors administering the procedure.

@@

Along any particular ray, monoenergetic particles will attenuate through a homogenous media according to the Beer-Lambert law given in Eq.~\ref{eq:beer_lambert} [CITE] resulting in a small fraction of the source particles reaching the detector. This phenomena leads to an image of the attenuating media but also results in the detector receiving information about the attenuation coefficient, $\mu$, along that ray. With sufficient rays of varying directionality, the entire object can be quantified with respect to its spatially distributed attenuation coefficient. The Hounsfield units (also called CT numbers) are traditionally scaled such that -1000 is dry air and water is zero [CITE].

@@

Deterministic codes can be accelerated with the use of a graphics processing unit (GPU). GPUs differ from the central processing unit (CPU) in that each of the many cores performs identical instruction to all others at the same time but each with different data. For example, consider a grayscale 1024$\times$768 image. If some pixelwise operation is applied on a CPU, 786,432 operations must occur. Onboard a GPU with 1024 cores, every pixel in the entire row can be computed simultaneously reducing the number of operations to 768. However, issues such as communication to and from the GPU and cache coherency problems can degrade performance. GPU technology and performance is discussed more thoroughly in Section~\ref{sec:cuda}.

In addition to rapidly computing the patient dose, another goal of DOCTORS is to present the code in a user-friendly fashion. To this end, a graphical user interface (GUI) was developed. The GUI utilize the Qt5 graphics framework for the window, buttons, and other necessary widgets. The GUI leads the user through the steps necessary to use the code in an intuitive way by using colors to indicated required and completed steps. The output is then plotted graphically as well as sent to an ASCII text file for more advanced postprocessing. More details about the GUI are included in Section~\ref{sec:gui}.
